Stellar Bars in Isolated Gas-Rich Galaxies Do Not Slow Down

### 2022-04-19 paper/ms.tex
Update some references

\begin{figure}[h]%
\centering
\includegraphics[width=0.45\textwidth]{fig/fig-vcirc.pdf}
\caption{The circular velocity curve for the N-body run (blue) and the SMUGGLE
run (orange) compared to observational estimates.\cite{2019ApJ...871..120E} We
see that the circular velocity curve for both runs is marginally larger than
the Milky Way's, but still comparable. The SMUGGLE circular velocity curve is
larger than the N-body curve due to the additional mass in the gas phase.}
\label{fig:surf}
\end{figure}

@@

\noindent
{\bf Bar analysis}
\\
\noindent
The analysis of various bar properties is performed as follows. First, the
pattern speed is measured from the angle of the second Fourier component. We measured the second Fourier component by computing,
\begin{equation}
\begin{split}
A_2 &= \sum_i m_i e^{i 2 \phi_i} \\
A_0 &= \sum_i m_i \textrm{,}
\end{split}
\end{equation}
where $m_i$ and $\phi_i$ are the mass and azimuthal angle of each particle, respectively. We
computed $A_2$ and $A_0$ in cylindrical bins of width $0.5\,\textrm{kpc}$ from radii of
$0$ to $30\,\textrm{kpc}$. We defined the angle of the bar $\phi_b$ to be
twice the angle of complex number $A_2$ as measured in the bin extending from
a radius of $2.5$ to $3\,\textrm{kpc}$. After correcting for the periodicity
of $\phi_b$, we measured the pattern speed as the two-sided finite gradient of
$\phi_b$ as a function of time.

@@

After the disk has been decomposed into a trapped and untrapped component, we
measured the bar length as being the radius $R_b$ which encapsulates $99\%$ of
the stars identified as being trapped in the bar, allowing for some outliers.
For the computation of the torque, we used the tree algorithm in
\texttt{MakeNewDisk} customized to be accessible from \texttt{Python} using
\texttt{Cython}. This algorithm is based on the \texttt{TREESPH} code. We
constructed a tree using only the star particles identified as being trapped
in the bar. We then queried the tree at the locations of all resolution
elements in the other components and computed the torque of the bar on such
components. The torque on the bar by the other components is simply the
negative of the torque on the other components by the bar. A similar method
was applied in measuring the torque for the disk when the pattern speed is
kept constant, as is done in Fig.~\ref{fig:equil}.

>>>>

\begin{figure}[h]%
\centering
\includegraphics[width=0.45\textwidth]{fig/fig-vcirc.pdf}
\caption{The circular velocity curve for the N-body run (blue) and the SMUGGLE
run (orange) compared to observational estimates.\cite{2019ApJ...871..120E} We
see that the circular velocity curve for both runs is marginally larger than
the Milky Way's, but still comparable. The SMUGGLE circular velocity curve is
larger than the N-body curve due to the additional mass in the gas phase.}
\label{fig:vcirc}
\end{figure}

@@

\noindent
{\bf Bar analysis}
\\
\noindent
The analysis of various bar properties is performed as follows. First, the
pattern speed is measured from the angle of the second Fourier component. We measured the second Fourier component by computing,
\begin{equation}
\begin{split}
A_2 &= \sum_i m_i e^{i 2 \phi_i} \\
A_0 &= \sum_i m_i \textrm{,}
\end{split}
\end{equation}
where $m_i$ and $\phi_i$ are the mass and azimuthal angle of each particle, respectively. We
computed $A_2$ and $A_0$ in cylindrical bins of width $0.5\,\textrm{kpc}$ from radii of
$0$ to $30\,\textrm{kpc}$. We defined the angle of the bar $\phi_b$ to be
twice the angle of the complex number $A_2$ as measured in the bin extending from
a radius of $2.5$ to $3\,\textrm{kpc}$. After correcting for the periodicity
of $\phi_b$, we measured the pattern speed as the two-sided finite gradient of
$\phi_b$ as a function of time.

@@

After the disk has been decomposed into a trapped and untrapped component, we
measured the bar length as being the radius $R_b$ which encapsulates $99\%$ of
the stars identified as being trapped in the bar, allowing for some outliers.
For the computation of the torque, we used the tree algorithm in
\texttt{MakeNewDisk}\cite{2005MNRAS.361..776S} customized to be accessible
from \texttt{Python} using \texttt{Cython}. This algorithm is based on the
\texttt{TREESPH} code.\cite{1989ApJS...70..419H} We constructed a tree using
only the star particles identified as being trapped in the bar using an
opening angle of $0.35$. We then queried the tree at the locations of all
resolution elements in the other components and computed the torque of the bar
on such components. The torque on the bar by the other components is simply
the negative of the torque on the other components by the bar. A similar
method was applied in measuring the torque for the disk when the pattern speed
is kept constant, as is done in Fig.~\ref{fig:equil}.
